Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-30 paper/aldebaran.tex
wording

For several reasons we are not convinced that this poses an issue for Aldebaran or for K~giant RV planets more generally. \citet{2018arXiv180105239H} suggest that the new type of stellar variability may be oscillatory convective modes, but both Aldebaran and Eltanin have much lower luminosities and longer periods than would seem to be allowed by the period-luminosity relation for these otherwise unobserved modes \citep[Figure~9]{2015MNRAS.452.3863S,2018arXiv180105239H}. If these are identified with the long secondary periods (LSPs) observed in some bright red giants ($L \approx 1000\, \lsun$), then Aldebaran and Eltanin are both too faint, and lack the mid-IR excess typical of LSP stars \citep{2009ApJ...707..573W}. It would also be surprising if the shape of the RV curve could reproduce the harmonic structure of an eccentric Keplerian such as in Aldebaran~b ($e = \EccentricityRange{}$), let alone the much higher eccentricities observed in other giants \citep[e.g. $\iota$~Dra~b, $e=0.7$:][]{2002ApJ...576..478F}.

>>>>

For several reasons we are not convinced that this poses an issue for Aldebaran or for K~giant RV planets more generally. \citet{2018arXiv180105239H} suggest that the new type of stellar variability may be oscillatory convective modes, but both Aldebaran and Eltanin have much lower luminosities and longer periods than would seem to be allowed by the period-luminosity relation predicted for these otherwise unobserved modes \citep[Figure~9]{2015MNRAS.452.3863S,2018arXiv180105239H}. If these are identified with the long secondary periods (LSPs) observed in some bright red giants ($L \approx 1000\, \lsun$), then Aldebaran and Eltanin are both too faint, and lack the mid-IR excess typical of LSP stars \citep{2009ApJ...707..573W}. It would also be surprising if the shape of the RV curve could reproduce the harmonic structure of an eccentric Keplerian such as in Aldebaran~b ($e = \EccentricityRange{}$), let alone the much higher eccentricities observed in other giants \citep[e.g. $\iota$~Dra~b, $e=0.7$:][]{2002ApJ...576..478F}.
